---
title: "The Mean of a Sampled Exponential Distribution"
output: pdf_document
---

We have collected 1000 means from 40 samplings of exponential distribution.  We then calculated the average, $\overline{\mu}$, and standard deviation, $\overline{\sigma}$, of those 1000 means.  Finally, we compared $\overline{\mu}$ and $\overline{\sigma}$ to the theoretical mean, $\mu$, and standard error, SE.  The standard error is the standard deviation of the exponential distribution divided by the square root of the number of samples, $\sigma/\sqrt{n}$.

```{r, echo=FALSE}
set.seed(80085)
options(digits=3)
```

The below analysis shows that the sample mean and the theoretical mean are statistically identical.
```{r}
lambda <- .2
MeanExpData <- replicate(1000, mean(rexp(40,lambda)))
print(paste0(sprintf('Sample mean: %.2f',mean(MeanExpData)), 
             sprintf(', Sample error: %.2f', sqrt(var(MeanExpData))), 
             sprintf(', Mean: %.2f', 1/lambda),
             sprintf(', Standard Error: %.2f', (1/lambda)/sqrt(40))))
```

You can also embed plots, for example:

```{r, echo=FALSE}

mew = mean(MeanExpData)
sig = sqrt(var(MeanExpData))

h_data <- hist(MeanExpData, freq = F, main = 'Histogram of Averaged Exponential Samples', xlab = 'Average of 40 Exponential Distribution Samples', breaks = 20)
abline(v = mean(MeanExpData), col = 'black', lty = 3)
abline(v = 5, col = 'red', lty = 3)

arrows(mean(MeanExpData), .52,mean(MeanExpData)-sqrt(var(MeanExpData)), .52, code = 3,length = .1)
arrows(mean(MeanExpData), .52,mean(MeanExpData)+sqrt(var(MeanExpData)), .52, code = 3,length = .1)

arrows(5, .31,5-5/sqrt(40), .31, code = 3,length = .1, col = 'red')
arrows(5, .31,5+5/sqrt(40), .31, code = 3,length = .1, col = 'red')

lines((0:100)/10, dnorm((0:100)/10, mean=5, sd = 5/sqrt(40)), col = 'red')

text(mew-.4, y = .55, labels = bquote(bar(mu)==.(mew)), col = 'black')
text(mew+.6 + sig, y = .52, labels = bquote(bar(mu)+bar(sigma)==.(mew + sig)), col = 'black')
text(mew-.6 - sig, y = .52, labels = bquote(bar(mu)-bar(sigma)==.(mew - sig)), col = 'black')
text(5+5/sqrt(40)+.65, y = .31, labels = bquote(mu+SE==.(5 + 5/sqrt(40))), col = 'red')
text(5-5/sqrt(40)-.6, y = .31, labels = bquote(mu-SE==.(5 - 5/sqrt(40))), col = 'red')
text(7.3, y = .2, labels = 'Gaussian Distribution', col = 'red')

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
